GSS Education Analysis (Working Title)

### 2023-03-16 outputs/paper/paper.qmd
fix in-text citation

All data within this paper are extracted from the 2021 United States General Social Survey (GSS). This survey consists of a series of nationally representative cross-sectional interviews and collects data on contemporary American society in order to explain trends in opinions, attitudes and behaviors and monitor these trends [@citegsscodebook**].** Since it began tracking trends in public opinion in 1972, the GSS has used in-person data collection as its primary method of data collection but in 2021, it moved to an address-based sampling method with a focus on web and web-based self-administered questionnaires **[@citegsscodebook**]. The 2021 GSS was conducted from December 1, 2020 to May 3, 2021, and was processed in accordance with standard NORC procedures [@citegsscodebook]**.**

>>>>

All data within this paper are extracted from the 2021 United States General Social Survey (GSS). This survey consists of a series of nationally representative cross-sectional interviews and collects data on contemporary American society in order to explain trends in opinions, attitudes and behaviors and monitor these trends [@citegsscodebook]. Since it began tracking trends in public opinion in 1972, the GSS has used in-person data collection as its primary method of data collection but in 2021, it moved to an address-based sampling method with a focus on web and web-based self-administered questionnaires [@citegsscodebook].The 2021 GSS was conducted from December 1, 2020 to May 3, 2021, and was processed in accordance with standard NORC procedures [@citegsscodebook]**.**
